---
title: "Integer programming"
author: "Pratheek Sreerangam"
date: "2022-11-20"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r comment=NA }
library(lpSolve)
library(lpSolveAPI)
y <- read.lp("ass11.lp")
y
```

Solving the problem to get objective function. 
```{r}
solve(y)
get.objective(y)
```
#Our Objective function is: 25675.
#Let's examine the factors to determine what this means.

```{r}
get.variables(y)
```


### What it illustrates is:
#Y1 = Sunday and Monday are off for shift 1 = 2
#Y2 = Monday and Tuesday are off for shift 2 = 4
#Y3 = Tuesday and Wednesday are off for shift 3= 5
#Y4 = Wednesday and Thursday are off for shift 4 = 0
#Y5 = Thursday and Friday are off for shift 5 = 8
#Y6 = Friday and Saturday are off for shift 6 = 1
#Y7 = Saturday and Sunday are off for shift 7 = 13

### Our objective function = 2x775 + 4x800 + 5x800 + 8x800 + 1X775 + 13x750 = 25675.
### The least amount we must spend on wages is $2675.


